An Air Drop That Preserves Recipient Privacy

### 2019-01-07 paper.tex
edits

Finally, it is not difficult to see that the computed $\Rv$ 
on line~\eqref{ln:computeR} is, with overwhelming probability,
the image under $\phi$ of some element $\rv' \in \range{2^{2\lambda}}^8$,
as in a real transcript.
{\bf TODO:} explain why.
\end{proof}

>>>>

Finally, because the simulated $c_1, c_2, \ell, \mathit{ch}, \Zv_q, \zv_\ell$
are all distributed statistically close to a real transcript, 
it must be the case that the computed $\Rv$ 
on line~\eqref{ln:computeR} is also distributed as in 
a real transcript. 
\end{proof}
